### 2019-07-26 paper/paper.tex
Update paper.tex

% JuliaCon proceedings template
\documentclass{juliacon}
\usepackage{amsmath}
\setcounter{page}{1}

@@

%%%%%%%%%%%%%%%%%%%%%%% Algorithm 1
\begin{listing}
\hline
\center{ \textbf{Pseudo-code for module Core.jl}}
\vspace{2mm}
\hline
  \begin{enumerate}

@@

    \item[2.] \textit{\textbf{function} gsreg\_proc\_results!(args…)}
    \begin{enumerate}
        \item[2.1.] \textbf{for} $j=1$ : $((k^2-1)/ nworkers)$ \textit{\# where nworkers is the user defined number of cores, and k is the numbers of ovariates %in the GUM}
        \begin{enumerate}
            \item[2.1.1.] $order = (j -1) * nworkers + workerID$
            \item[2.1.2.] \textit{gsreg\_single\_proc\_results!(order, args...)}
        \end{enumerate}
        \item[] \textbf{end} for
    \end{enumerate}
    \item[] \textbf{end} \textit{function gsreg\_single\_proc\_results!(args…)}

@@

\begin{flushleft}
\textbf{end} module \verb Core.jl . \hfill
\end{flushleft}
\hline
\end{listing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

% JuliaCon proceedings template
\documentclass{juliacon}
\usepackage{amsmath}
\usepackage{algorithm}
\setcounter{page}{1}

@@

\begin{algorithm}[ht]
  \scriptsize
  \caption{module Core.jl}
  \begin{enumerate}

@@

    \item[2.] \textit{\textbf{function} gsreg\_proc\_results!(args…)}
    \begin{enumerate}
        \item[2.1.] \textbf{for} $j=1$ : $((k^2-1)/ nworkers)$ \textit{\# where nworkers is the user defined number of cores, and k is the numbers of covariates in the GUM}
        \begin{enumerate}
            \item[2.1.1.] $order = (j -1) * nworkers + workerID$
            \item[2.1.2.] \textit{gsreg\_single\_proc\_results!(order, args...)}
        \end{enumerate}
        \item[] \textbf{end} for
    \end{enumerate}
    \item[] \textbf{end} \textit{function gsreg\_single\_proc\_results!(args…)}

@@

\textbf{end} module \verb Core.jl .
\end{algorithm}
